Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-20 appendix.qmd
Added initial image for Figure 5

```{r}
#| label: read-pbmc-umap-layouts
# Read a variety of different NLDR representations of PBMC
# and plot them on same aspect ratio
umap_pbmc1 <- read_rds("data/pbmc3k/pbmc_scdeed_umap_n_neighbors_30_min_dist_0.3.rds")
umap_pbmc1 <- as_tibble(umap_pbmc1)
names(umap_pbmc1) <- c("UMAP1", "UMAP2")

nldr1c <- umap_pbmc1 |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("a")

umap_pbmc2 <- read_rds("data/pbmc3k/pbmc_scdeed_umap_n_neighbors_80_min_dist_0.5.rds")
umap_pbmc2 <- as_tibble(umap_pbmc2)
names(umap_pbmc2) <- c("UMAP1", "UMAP2")

nldr2c <- umap_pbmc2 |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1, colour='#377eb8') +
  interior_annotation("b")

@@

```{r}
#| label: combine-data-pbmc-umap

error_pbmc_umap <- read_rds("data/pbmc3k/error_scdeed_pbmc_umap_30_min_dist_0.3.rds")
error_pbmc_umap2 <- read_rds("data/pbmc3k/error_scdeed_pbmc_umap_80_min_dist_0.5.rds")

error_pbmc <- bind_rows(error_pbmc_umap,
                        error_pbmc_umap2)

@@

error_umap_plot_pbmc <-  plot_mse(error_pbmc) +
  scale_x_continuous(breaks = sort(unique(error_pbmc$a1))[c(1, 5, 9, 12, 15, 17, 19, 20)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8'))
```

@@

```{r}
#| label: published-pbmc-scdeed

training_data_pbmc <- read_rds("data/pbmc3k/pbmc_pca_50_scdeed.rds")
training_data_pbmc <- training_data_pbmc[, 1:50] |>
  mutate(ID = 1:NROW(training_data_pbmc))

## For umap
umap_pbmc <- read_rds("data/pbmc3k/pbmc_scdeed_umap_n_neighbors_80_min_dist_0.5.rds")
umap_pbmc <- as_tibble(umap_pbmc)
names(umap_pbmc) <- c("UMAP1", "UMAP2")
umap_pbmc <- umap_pbmc |>
  mutate(ID = 1:NROW(umap_pbmc))

pbmc_scaled_obj_umap <- gen_scaled_data(
  data = umap_pbmc)
umap_pbmc_scaled <- pbmc_scaled_obj_umap$scaled_nldr

lim1 <- pbmc_scaled_obj_umap$lim1
lim2 <- pbmc_scaled_obj_umap$lim2
r2_umap <- diff(lim2)/diff(lim1)

```{r}
#| label: hexbin-pbmc-scdeed

## Compute hexbin parameters
num_bins_x_pbmc <- 12
lim1 <- pbmc_scaled_obj_umap$lim1
lim2 <- pbmc_scaled_obj_umap$lim2
r2_pbmc <- diff(lim2)/diff(lim1)

pbmc_model <- fit_highd_model(
    highd_data = training_data_pbmc,
    nldr_data = umap_pbmc_scaled,
    bin1 = num_bins_x_pbmc,
    r2 = r2_pbmc,
    q = 0.1,
    is_bin_centroid = TRUE
  )

df_bin_centroids_pbmc <- pbmc_model$df_bin_centroids
df_bin_pbmc <- pbmc_model$df_bin

## Triangulate bin centroids
tr1_object_pbmc <- tri_bin_centroids(
  df_bin_centroids_pbmc, x = "c_x", y = "c_y")
tr_from_to_df_pbmc <- gen_edges(
  tri_object = tr1_object_pbmc)

## Compute 2D distances
distance_pbmc <- cal_2d_dist(
  tr_coord_df = tr_from_to_df_pbmc,
  start_x = "x_from",
  start_y = "y_from",
  end_x = "x_to",
  end_y = "y_to",
  select_vars = c("from", "to", "distance"))

## To find the benchmark value
benchmark_pbmc <- find_lg_benchmark(
  distance_edges = distance_pbmc,
  distance_col = "distance")

tr_df <- distinct(tibble(
  x = c(tr_from_to_df_pbmc[["x_from"]], tr_from_to_df_pbmc[["x_to"]]),
  y = c(tr_from_to_df_pbmc[["y_from"]], tr_from_to_df_pbmc[["y_to"]])))

distance_df_small_edges_pbmc <- distance_pbmc |>
  filter(distance < benchmark_pbmc)

tr_from_to_df_pbmc <- inner_join(
  tr_from_to_df_pbmc, distance_df_small_edges_pbmc,
  by = c("from", "to"))

trimesh_removed_pbmc <- ggplot() +
  geom_segment(data = tr_from_to_df_pbmc,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  geom_point(
    data = umap_pbmc_scaled,
    aes(
      x = UMAP1,
      y = UMAP2
    ),
    alpha = 0.2,
    color = '#a65628'
  )  +
  interior_annotation("a1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

```{r}
#| label: pbmc-umap-model-proj-scdeed

@@

scaled_pbmc_data_model <- scaled_pbmc |>
  filter(type == "model") |>
  select(-type)

# Combine with the true model for visualization
df <- dplyr::bind_rows(scaled_pbmc_data_model |> mutate(type = "model"),
                       scaled_pbmc_data |> mutate(type = "data"))

## First projection
projection <- cbind(
  c(0.040856,0.000723,0.006000,0.007623,0.001986,-0.006599,0.005311,-0.000222,0.001648,0.008067,-0.001587,0.004423,0.004851,0.000638,0.002606,0.006616,0.006188,-0.000954,-0.004603,0.004998,-0.012220,0.008401,-0.007788,0.008972,-0.003903,0.003348,-0.001817,-0.000385,-0.002437,-0.004097,-0.001357,0.013660,0.001770,0.006982,0.002828,-0.009169,-0.003541,0.008582,-0.000032,-0.002375,0.005854,-0.005466,-0.000824,-0.001435,0.004148,0.007141,0.000883,-0.004159,0.005401,0.007882),
  c(-0.000590,0.039365,-0.004481,-0.009041,-0.003805,0.003278,-0.009601,-0.000650,-0.002333,-0.005697,-0.001488,-0.009808,0.002557,0.004113,0.005705,-0.004665,-0.001170,-0.004727,-0.000845,0.005084,-0.018054,0.002538,0.006606,-0.007184,0.000238,0.001877,-0.002124,-0.005972,-0.009729,0.004958,-0.003181,-0.005185,-0.009598,-0.004243,0.007716,0.000396,-0.004258,0.005932,-0.003242,-0.004184,0.003493,-0.008405,0.000860,0.008304,0.004569,0.000798,0.004156,-0.005777,0.005278,-0.002531))

projection_scaled <- projection * 3

projected <- as.matrix(scaled_pbmc_data) %*% projection_scaled

projected_df <- projected |>
  tibble::as_tibble(.name_repair = "unique") |>
  dplyr::rename(c("proj1" = "...1",
                  "proj2" = "...2")) |>
  #dplyr::mutate(type = df_exe$type) |>
  dplyr::mutate(ID = dplyr::row_number())

projected_model <- as.matrix(scaled_pbmc_data_model) %*% projection_scaled

projected_model_df <- projected_model |>
  tibble::as_tibble(.name_repair = "unique") |>
  dplyr::rename(c("proj1" = "...1",
                  "proj2" = "...2")) |>
  dplyr::mutate(ID = dplyr::row_number())

model_df <- dplyr::left_join(
  distance_df_small_edges_pbmc |> select(-distance),
  projected_model_df,
  by = c("from" = "ID"))

names(model_df)[3:NCOL(model_df)] <- paste0(names(projected_model_df)[-NCOL(projected_model_df)], "_from")

model_df <- dplyr::left_join(model_df, projected_model_df, by = c("to" = "ID"))
names(model_df)[(2 + NCOL(projected_model_df)):NCOL(model_df)] <- paste0(names(projected_model_df)[-NCOL(projected_model_df)], "_to")

axes_obj <- gen_axes(
  proj = projection,
  limits = 0.04,
  axis_pos_x = -0.025,
  axis_pos_y = -0.025,
  axis_labels = names(scaled_pbmc_data),
  threshold = 0.0001)

axes <- axes_obj$axes
circle <- axes_obj$circle

pbmc_proj_umap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1,
      y = proj2)) +
  geom_segment(
    data = model_df,
    aes(
      x = proj1_from,
      y = proj2_from,
      xend = proj1_to,
      yend = proj2_to),
    color = "#000000") +
  geom_point(
    #size = 0.5,
    alpha = 0.2,
    color = '#a65628') +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2),
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle,
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.03, 0.06)) +
  ylim(c(-0.03, 0.06)) +
  interior_annotation("a2", cex = 2)

## Second projection
projection <- cbind(
  c(-0.019825,-0.011101,0.011543,-0.006943,-0.004485,0.000062,0.002023,-0.005178,0.000800,-0.002903,-0.014182,0.008756,0.009595,0.007032,-0.007820,0.006143,0.004865,0.003352,0.007554,0.002265,0.012035,0.009961,-0.001825,-0.004942,-0.002237,0.002308,0.009531,-0.001146,0.013401,-0.001022,0.008434,0.000477,0.004239,-0.006772,-0.004702,-0.011432,-0.000431,0.008146,-0.009299,-0.004782,0.003457,-0.008214,-0.009604,0.011329,0.003805,-0.003004,-0.000800,0.015288,-0.013157,0.006984),
  c(-0.001387,0.001643,0.010470,0.002930,-0.002335,-0.010569,0.013839,0.002917,-0.006825,0.010191,-0.006367,0.002220,0.002506,0.005139,-0.007213,-0.006235,-0.007123,-0.000222,-0.002225,0.011592,-0.003942,0.002788,-0.000055,0.011316,-0.009753,0.020785,0.004615,0.005172,0.011182,-0.003125,-0.010860,0.007820,-0.017510,0.007010,0.007267,0.002694,-0.003949,-0.009188,-0.005163,0.001898,-0.004744,0.013757,0.010630,-0.007688,0.004598,0.004658,-0.011154,0.003584,-0.005226,0.006650))

projection_scaled <- projection * 3

projected <- as.matrix(scaled_pbmc_data) %*% projection_scaled

projected_df <- projected |>
  tibble::as_tibble(.name_repair = "unique") |>
  dplyr::rename(c("proj1" = "...1",
                  "proj2" = "...2")) |>
  #dplyr::mutate(type = df_exe$type) |>
  dplyr::mutate(ID = dplyr::row_number())

projected_model <- as.matrix(scaled_pbmc_data_model) %*% projection_scaled

projected_model_df <- projected_model |>
  tibble::as_tibble(.name_repair = "unique") |>
  dplyr::rename(c("proj1" = "...1",
                  "proj2" = "...2")) |>
  dplyr::mutate(ID = dplyr::row_number())

model_df <- dplyr::left_join(
  distance_df_small_edges_pbmc |> select(-distance),
  projected_model_df,
  by = c("from" = "ID"))

names(model_df)[3:NCOL(model_df)] <- paste0(names(projected_model_df)[-NCOL(projected_model_df)], "_from")

model_df <- dplyr::left_join(model_df, projected_model_df, by = c("to" = "ID"))
names(model_df)[(2 + NCOL(projected_model_df)):NCOL(model_df)] <- paste0(names(projected_model_df)[-NCOL(projected_model_df)], "_to")

axes_obj <- gen_axes(
  proj = projection,
  limits = 0.03,
  axis_pos_x = -0.02,
  axis_pos_y = -0.02,
  axis_labels = names(scaled_pbmc_data),
  threshold = 0)

axes <- axes_obj$axes
circle <- axes_obj$circle

pbmc_proj_umap_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1,
      y = proj2)) +
  geom_segment(
    data = model_df,
    aes(
      x = proj1_from,
      y = proj2_from,
      xend = proj1_to,
      yend = proj2_to),
    color = "#000000") +
  geom_point(
    #size = 0.5,
    alpha = 0.2,
    color = '#a65628') +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2),
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle,
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.025, 0.02)) +
  ylim(c(-0.025, 0.02)) +
  interior_annotation("a3", cex = 2)
```

```{r}
#| fig-cap: "Model in \\gD{}, on the layout a, and two views of the fit in projections from $50\\text{-}D$, for the PBMC data ($n =  5858$ and $p = 50$). Layout shows close clusters. In $50\\text{-}D$, the data shows "
#| label: fig-model-pbmc-author-proj-scdeed
#| fig-pos: H
#| fig-width: 15
#| fig-height: 5
#| out-width: 30%

free(trimesh_removed_pbmc) +
  pbmc_proj_umap_model1 +
  pbmc_proj_umap_model2 +
  plot_layout(ncol=3) &
  theme(legend.position='none')
```

>>>>

```{r}
#| label: read-pbmc-umap-layouts
# Read a variety of different NLDR representations of PBMC
# and plot them on same aspect ratio
umap_pbmc <- read_rds("data/pbmc3k/pbmc_scdeed_umap_n_neighbors_30_min_dist_0.3.rds")
umap_pbmc <- as_tibble(umap_pbmc)
names(umap_pbmc) <- c("emb1", "emb2")
umap_pbmc <- umap_pbmc |>
  dplyr::mutate(ID = row_number())

nldr1c <- umap_pbmc |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("a")

tsne_pbmc <- read_rds("data/pbmc3k/pbmc_scdeed_tsne_perplexity_30.rds")
tsne_pbmc <- as_tibble(tsne_pbmc)
names(tsne_pbmc) <- c("emb1", "emb2")
tsne_pbmc <- tsne_pbmc |>
  dplyr::mutate(ID = row_number())

nldr2c <- tsne_pbmc |>
  ggplot(aes(x = emb1,
             y = emb2))+
  geom_point(alpha=0.1, size=1, colour='#377eb8') +
  interior_annotation("b")

@@

```{r}
#| label: combine-data-pbmc-umap-tsne

error_pbmc_umap <- read_rds("data/pbmc3k/error_scdeed_pbmc_umap_30_min_dist_0.3.rds")
error_pbmc_tsne <- read_rds("data/pbmc3k/error_scdeed_pbmc_tsne_perplexity_30.rds")

error_pbmc <- bind_rows(error_pbmc_umap,
                        error_pbmc_tsne)

@@

error_umap_plot_pbmc <-  plot_mse(error_pbmc) +
  scale_x_continuous(breaks = sort(unique(error_pbmc$a1))[c(1, 5, 9, 12, 15, 17, 19, 20)]) +
  scale_color_manual(values=c('#377eb8', '#e41a1c'))
```

@@

```{r}
#| label: hexbin-pbmc
training_data_pbmc <- read_rds("data/pbmc3k/pbmc_pca_50_scdeed.rds")
training_data_pbmc <- training_data_pbmc[, 1:9] |>
  mutate(ID = 1:NROW(training_data_pbmc))

names(training_data_pbmc) <- append(paste0("x", 1:9), "ID")

## Compute hexbin parameters
num_bins_x_pbmc <- 22

algo_obj_pbmc <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_pbmc, 
  nldr_data = umap_pbmc, 
  num_x_bins = num_bins_x_pbmc)

umap_pbmc_scaled <- algo_obj_pbmc$nldr_scaled
distance_pbmc <- algo_obj_pbmc$distance_df
tr_from_to_df_pbmc <- algo_obj_pbmc$tr_from_to_df
benchmark_pbmc <- algo_obj_pbmc$benchmark
df_bin_centroids_pbmc <- algo_obj_pbmc$df_bin_centroids
df_bin_pbmc <- algo_obj_pbmc$df_bin

distance_df_small_edges_pbmc <- distance_pbmc |>
  filter(distance < benchmark_pbmc)#benchmark_pbmc

umap_pbmc_scaled_with_cluster <- umap_pbmc_scaled |>
  mutate(cluster = if_else(emb1 <= 0.3, "cluster1", if_else((emb1 >= 0.75) & (emb2 <= 0.25), "cluster3", "cluster2"))) |>
  mutate(cluster = factor(cluster, levels = c("cluster1", "cluster2", "cluster3")))

tr_from_to_df_pbmc <- right_join(
  tr_from_to_df_pbmc, distance_df_small_edges_pbmc, 
  by = c("from", "to"))

trimesh_removed_pbmc <- ggplot() + 
  geom_point(
    data = umap_pbmc_scaled_with_cluster,
    aes(
      x = emb1,
      y = emb2,
      color = cluster
    ),
    alpha = 0.2,
    size = 0.1
  )  +
  geom_segment(data = tr_from_to_df_pbmc, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada")) +
  interior_annotation("a1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

```{r}
#| label: prep-pbmc-umap-model-proj

@@

scaled_pbmc_data_model <- scaled_pbmc |>
  filter(type == "model") |>
  select(-type)
```

```{r}
#| label: langevitour-pbmc-umap-author-proj
#| eval: false

data_pbmc_n <- data_pbmc |>
  select(-type) |>
  mutate(type = as.character(umap_pbmc_scaled_with_cluster$cluster))

df_model_data_pbmc_n <- bind_rows(df_b_pbmc, data_pbmc_n)

langevitour::langevitour(df_model_data_pbmc_n[1:(length(df_model_data_pbmc_n)-1)],
                         lineFrom = distance_df_small_edges_pbmc$from,
                         lineTo = distance_df_small_edges_pbmc$to,
                         group = factor(df_model_data_pbmc_n$type,
                                        c("cluster1", "cluster2", "cluster3", "model")),
                         levelColors = c("#8dd3c7", "#fdb462", "#bebada", "#000000"))
```

```{r}
#| label: pbmc-umap-model-proj

## First projection
projection <- cbind(
    c(-0.4545,-0.5533,-0.1235,0.3984,-0.2065,-0.3586,-0.0088,0.3572,-0.1368),
    c(0.4576,-0.3157,0.4708,0.1410,-0.4479,-0.1685,0.3668,-0.2692,0.1332))

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 1.23, 
               scaled_data = scaled_pbmc_data, 
               scaled_data_model = scaled_pbmc_data_model, 
               distance_df_small_edges = distance_df_small_edges_pbmc, 
               axis_param = list(limits = 1,
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.48, 
                                 axis_pos_y = -0.48, 
                                 threshold = 0.082))

proj_obj1[["cluster"]] <- as.character(umap_pbmc_scaled_with_cluster$cluster)

pbmc_proj_umap_model1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.65, 0.65), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

## Second projection
projection <- cbind(
    c(0.0734,0.6138,-0.4671,0.2589,0.1189,0.0778,-0.0819,0.0308,-0.5561),
    c(0.6625,0.0034,0.2412,0.3360,0.2463,0.1070,-0.2903,-0.4705,0.1293))

proj_obj2 <- get_projection(projection = projection, 
               proj_scale = 1.25, 
               scaled_data = scaled_pbmc_data, 
               scaled_data_model = scaled_pbmc_data_model, 
               distance_df_small_edges = distance_df_small_edges_pbmc, 
               axis_param = list(limits = 1.35, 
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.75, 
                                 axis_pos_y = -0.75, 
                                 threshold = 0.12))

proj_obj2[["cluster"]] <- as.character(umap_pbmc_scaled_with_cluster$cluster)

pbmc_proj_umap_model2 <- plot_proj(
    proj_obj = proj_obj2, 
    point_param = c(1.5, 0.2), # size, alpha, color
    plot_limits = c(-1, 0.75), 
    title = "a3", 
    cex = 2, 
    axis_text_size = 4,
    is_color = TRUE) + scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

```{r}
#| label: hexbin-pbmc2

## Compute hexbin parameters
num_bins_x_pbmc <- 22

algo_obj_pbmc <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_pbmc, 
  nldr_data = tsne_pbmc, 
  num_x_bins = num_bins_x_pbmc)

tsne_pbmc_scaled <- algo_obj_pbmc$nldr_scaled
distance_pbmc <- algo_obj_pbmc$distance_df
tr_from_to_df_pbmc <- algo_obj_pbmc$tr_from_to_df
benchmark_pbmc <- algo_obj_pbmc$benchmark
df_bin_centroids_pbmc <- algo_obj_pbmc$df_bin_centroids
df_bin_pbmc <- algo_obj_pbmc$df_bin

distance_df_small_edges_pbmc <- distance_pbmc |>
  filter(distance < benchmark_pbmc)#benchmark_pbmc

tsne_pbmc_scaled_with_cluster <- tsne_pbmc_scaled |>
  mutate(cluster = if_else((emb1 <= 0.4) & (emb2 <= 0.6), "cluster1", if_else((emb1 >= 0.75) & (emb2 <= 0.25), "cluster3", "cluster2"))) |>
  mutate(cluster = factor(cluster, levels = c("cluster1", "cluster2", "cluster3")))

tr_from_to_df_pbmc <- right_join(
  tr_from_to_df_pbmc, distance_df_small_edges_pbmc, 
  by = c("from", "to"))

trimesh_removed_pbmc_best <- ggplot() + 
  geom_point(
    data = tsne_pbmc_scaled_with_cluster,
    aes(
      x = emb1,
      y = emb2,
      color = cluster
    ),
    alpha = 0.2,
    size = 0.1
  )  +
  geom_segment(data = tr_from_to_df_pbmc, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada")) +
  interior_annotation("a1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

```{r}
#| label: prep-pbmc-tsne-model-proj-best

scaled_pbmc_data_model <- scaled_pbmc |>
  filter(type == "model") |>
  select(-type)
```

```{r}
#| label: langevitour-pbmc-tsne-author-proj-best
#| eval: false

data_pbmc_n <- data_pbmc |>
  select(-type) |>
  mutate(type = as.character(tsne_pbmc_scaled_with_cluster$cluster))

df_model_data_pbmc_n <- bind_rows(df_b_pbmc, data_pbmc_n)

langevitour::langevitour(df_model_data_pbmc_n[1:(length(df_model_data_pbmc_n)-1)],
                         lineFrom = distance_df_small_edges_pbmc$from,
                         lineTo = distance_df_small_edges_pbmc$to,
                         group = factor(df_model_data_pbmc_n$type,
                                        c("cluster1", "cluster2", "cluster3", "model")),
                         levelColors = c("#8dd3c7", "#fdb462", "#bebada", "#000000"))
```

```{r}
#| label: pbmc-tsne-model-proj-best

## First projection
projection <- cbind(
  c(-0.4545,-0.5533,-0.1235,0.3984,-0.2065,-0.3586,-0.0088,0.3572,-0.1368),
  c(0.4576,-0.3157,0.4708,0.1410,-0.4479,-0.1685,0.3668,-0.2692,0.1332))

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.23, 
                            scaled_data = scaled_pbmc_data, 
                            scaled_data_model = scaled_pbmc_data_model, 
                            distance_df_small_edges = distance_df_small_edges_pbmc, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 1, 
                                              axis_pos_x = -0.48, 
                                              axis_pos_y = -0.48, 
                                              threshold = 0.082))

proj_obj1[["cluster"]] <- as.character(tsne_pbmc_scaled_with_cluster$cluster)

pbmc_proj_tsne_model1_best <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.65, 0.65), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

## Second projection
projection <- cbind(
  c(0.0734,0.6138,-0.4671,0.2589,0.1189,0.0778,-0.0819,0.0308,-0.5561),
  c(0.6625,0.0034,0.2412,0.3360,0.2463,0.1070,-0.2903,-0.4705,0.1293))

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.25, 
                            scaled_data = scaled_pbmc_data, 
                            scaled_data_model = scaled_pbmc_data_model, 
                            distance_df_small_edges = distance_df_small_edges_pbmc, 
                            axis_param = list(limits = 1.35, 
                                              axis_scaled = 1, 
                                              axis_pos_x = -0.75, 
                                              axis_pos_y = -0.75, 
                                              threshold = 0.12))

proj_obj2[["cluster"]] <- as.character(tsne_pbmc_scaled_with_cluster$cluster)

pbmc_proj_tsne_model2_best <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1, 0.75), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

```{r}
#| echo: false
#| fig-cap: ""
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-width: 90%

free(trimesh_removed_pbmc) + free(trimesh_removed_pbmc_best) +
  pbmc_proj_umap_model1 + pbmc_proj_tsne_model1_best +
  pbmc_proj_umap_model2 + pbmc_proj_tsne_model2_best +
  plot_layout(nrow=2, byrow=FALSE) &
  theme(legend.position='none')
```
